### 2023-11-12 manuscript/manuscript.Rmd
Fix sentence structure

The use of correlations to identify relationships between *m/z* features provides an essential layer of data-driven, internal validation of theoretically derived associations.
For instance, if two features are posited to have the same molecular formula based on a mass difference equivalent to ^13^C but are not significantly correlated within the matrix, it would then be illogical to infer biological assumptions about other associations (eg. metabolic pathway changes) of those features with other putatively assigned features within the matrix.

>>>>

The use of correlations to identify relationships between *m/z* features provides an essential layer of data-driven, internal validation of theoretically derived associations.
For instance, if two features are posited to have the same molecular formula based on a mass difference equivalent to ^13^C but are not significantly correlated within the matrix, it would then be illogical to infer biological assumptions about associations (eg. metabolic pathway changes) with other putatively assigned features.
